---
title: "Learning the basics of ggplot and use of color."
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Intro

In this blog I will show you the basics to making and formatting a ggplot with color. I will go over introductory steps to make these plots, which will cover very basic skills, and overall help understand how to format these plots better using color.   

## Tutorial

You will first need to install and load the **ggplot2** package in R:

```
install.packages("ggplot2")
library(ggplot2)
```

To see our data set I will need to first install and load **knitr** package in R:

```
install.packages("knitr")
library(knitr)
```

To see our table we will - 

```
head(mtcars)
```
``` {r, echo = FALSE, results = 'axis'}
library(knitr)
kable(mtcars[1:5, ])

```

## Making simple plots - 

```
ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point()
```

``` {r, echo = FALSE}
library(ggplot2)
library(MASS)
ggplot(mtcars, aes(x=wt, y=mpg)) + geom_point()
```

## Using a single color in your plot - 

```
ggplot(mtcars, aes(x=wt, y=mpg)) + 
  geom_point(color='darkblue')
```

``` {r, echo = FALSE}
library(ggplot2)
ggplot(mtcars, aes(x=wt, y=mpg)) + 
  geom_point(color='darkblue')
```

## Change colors by groups - 

```
sp<-ggplot(mtcars, aes(x=wt, y=mpg, color=cyl)) + geom_point()
sp
```

``` {r, echo = FALSE}
library(ggplot2)
sp <- ggplot(mtcars, aes(x=wt, y=mpg, color=cyl)) + geom_point()
sp
```

## To make a different color scheme manually - 

```
ggplot(mtcars, aes(x=wt, y=mpg, color=as.factor(cyl))) + geom_point() + scale_color_manual(values=c('#999999','#E69F00', '#56B4E9'))
```

``` {r, echo = FALSE}
ggplot(mtcars, aes(x=wt, y=mpg, color=as.factor(cyl))) + geom_point() + scale_color_manual(values=c('#999999','#E69F00', '#56B4E9'))
```












